\documentclass[a4paper]{article}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}


\setlength{\parindent}{0pt}

\title{\textbf{Curriculum Vitae}}
\date{\today}
\begin{document}

\maketitle
\thispagestyle{empty}

\textbf{Name:} Tomas Bjerre \\
\textbf{Social security number:} 851209-XXXX \\
\textbf{Gender:} Male \\
\textbf{Address:} Arklim\"astaregatan 30, 37135 Karlskrona, SWEDEN \\
\textbf{E-mail:} \texttt{tomas.bjerre85@gmail.com} \\
\textbf{WWW:} \texttt{http://www.tomasbjerre.se/} \\

\section*{Personal qualities}
I am a software developer. I have been doing full stack development since 2010, in different Java projects. I have a special interest in continuous integration and tools development.

I enjoy working out on my spare time and will consider it a big advantage if my client offers a health center. I also enjoy being social with friends, watch movies and play video games. I also have an interest in stock trading and I strongly believe that money should be invested, before it is gone.

I am committed and dedicated to any task I am assigned. I can work under pressure, independently or in a group. I am imaginative and creative as well as competent. I like to work methodical and I like well structured and complete solutions.

I enjoy developing software on my spare time. I host most of my own projects on GitHub. I have started, and contributed to, many open source projects used by thousands of companies and hundreds of thousands developers.

\newpage

\section*{Open source}
I'm a Jenkins plugin committer, founder/maintainer of these plugins:

\begin{itemize}
 \item \textbf{Generic Webhook Trigger Plugin}
 \item \textbf{Git Changelog Plugin}
 \item \textbf{Violation Comments to GitLab Plugin}
 \item \textbf{Violation Comments to GitHub Plugin}
 \item \textbf{Violation Comments to Bitbucket Server Plugin}
\end{itemize}

I also have some mixed projects on my GitHub.


\section*{Education}
\textbf{Master of Science in Computer Engineering}, Lund University, Faculty of Engineering, Lund, 2004-2009. \\
\textbf{High school (Teknikprogrammet)}, Knut Hahn, Ronneby, 2001-2004. \\
\textbf{Drivers license} A1, A2, A3, A4, B, B2 and B3. \\
\newpage


\section*{Work experience}
\begin{itemize}
  \item \textbf{Forsakringskassan (Swedish Social Insurance Agency)} 2019-04-01 to present \\
  Frontend technologies, among others, TypeScript, JavaScript, VueJS, AngularJS, NodeJS/NPM, Cypress, HTML, CSS, AJAX, OpenAPI.

  Native IOS/Android app development with, among others, TypeScript and NativeScript Vue.
  
  Backend development with, among others, Java, Groovy, Gradle, SpringBoot, Spring, REST, CI/CD with Jenkins, Jenkins Pipelines, OpenShift / Kubernetes, Nexus, Git, Bitbucket, Linux, OpenAPI.
  
  Fullstack software developer in teams with mixed responsibilities. Working with developing frontend, backend (REST) as well as native IOS/Android.
  
  Was assigned extra time to spend on tools development. Spent on, among other things, prototyping and introducing patterns in Gradle, Jenkins and Node. Things that I have also blogged and shared:

  \begin{itemize}
    \item https://github.com/tomasbjerre/gradle-scripts
    \item https://www.jenkins.io/blog/2020/10/21/a-sustainable-pattern-with-shared-library/
  \end{itemize}
  
  Introduced OpenAPI and formal specifications of REST API:s along with a tool chain supporting that workflow.
  
  Was part of a CM team. Responsible for packaging and delivering as well as developing the tools, and processes, needed for that to work smoothly.
\end{itemize}
  

\begin{itemize}
 \item \textbf{Tomas Bjerre AB} 2017-07-01 to 2019-04-01 \\
 Freelance software engineer.
 \begin{itemize}
  \item \textbf{Jordbruksverket (Swedish Board of Agriculture)} 2018-10-01 to 2019-04-01 \\
  Work involving: Java, Groovy, Drools, JBoss, A-MQ, JMS, Maven 3, Jenkins, Jenkins Pipelines, CQRS, Event Sourcing, SOA, JAXB, PostgreSQL, Angular, TypeScript, AngularJS, LESS, Docker, Wiremock, REST Assured, Test Automation, BDD, TDD, SOA, Visual Studio Code, Eclipse.

  Was part of a platforms team maintaining and developing a software platform for several other systems. Doing major refactorings, developing tools and making sure developers using the platform can work effectively. Migrated apps from Javascript and AngularJS to TypeScript and Angular.

  \item \textbf{Domstolsverket (Swedish National Courts Administration)} 2018-01-01 to 2010-09-30 \\
  Work involving: Java, Groovy, JBoss (Wildfly), Weblogic, Maven, Jenkins, Jenkins Pipelines, Artifactory, Nexus IQ Server (Lifecycle), Sonar, Git, Bitbucket Server.

  Installed a new Jenkins with agents and created pipelines for 100+ repositories. Using shared libraries to eliminate duplicated code. Automatic creation of all necessary jobs (snapshot, release, pull-requests, releasenotes, sonar and orchestration of release/snapshot) synchronized with Bitbucket Server using Job DSL and Pipelines. Even autmoatic calculation of dependencies among repositories so that the release process is automatically performed in correct order based on what repositories to release.
  \item \textbf{Jordbruksverket (Swedish Board of Agriculture)} 2017-07-01 to 2017-12-31 \\
  Work involving: Java, Groovy, Drools, JBoss, A-MQ, JMS, Maven 3, Jenkins, Jenkins Pipelines, CQRS, Event Sourcing, SOA, JAXB, PostgreSQL, AngularJS, LESS, Docker, Citrus, REST Assured, Test Automation, BDD, TDD, SOA, Eclipse.

  Was part of feature teams, implementing features based on requirement specifications and fixing bugs.

  Spent the last year in a QA team working on technical improvements of the system. Setting up verification of merge requests with GitLab and Jenkins (Compiling, Unit testing, FitNesse testing, Smoketest in Docker, Static code analysis). Doing several major refactorings.
 \end{itemize}
\end{itemize}
  
\begin{itemize}
 \item \textbf{SoftHouse} 2010-01-01 to 2017-06-30 \\
 Software engineer consultant.
 \begin{itemize}
  \item \textbf{Jordbruksverket (Swedish Board of Agriculture)} 2015-08-17 to 2017-06-30 \\
  See above.
  
  \item \textbf{Forsakringskassan (Swedish Social Insurance Agency)} 2014-09-15 to 2015-08-15 \\
  Development of forsakringskassan.se. Using, among other technologies, Java, Javascript (Dojo), CSS, Websphere, Websphere Portal, Gradle, GIT, Jenkins, Stash. Doing a lot of scripting (Groovy) in Jenkins to automate tasks and integrate it with Stash to, among other things, build pull requests.
  
  \item \textbf{Aditro} 2014-06-23 to 2014-09-15 \\
  Work involving: AngularJS and .NET. Mainly doing front end development.
  Developing software for administration of employees.
  
  \item \textbf{IST International Software Technology AB} 2014-01-01 to 2014-06-20 \\
  Work involving: Java (Spring Framework, Tomcat, JUnit, JBehave, H2, ANT, Maven, Guava), Eclipse, Subversion, GIT, Gerrit, Hudson, Jenkins, BDD, TDD, REST, Angular JS, Eclipse. \\
  Developing software that is used for administration in schools. A module exposing and using API:s, intended to be used by administrators. A portal, Angular JS, intended to be used by students.
  
  \item \textbf{Boss Media AB} 2013-03-01 to 2013-12-31 \\
  Work involving: Java (Spring Framework, JBoss, JUnit, TestNG, EasyMock, JVisualVM, ANT, Ivy, Gson, Guava), Eclipse, Subversion, Jenkins, TDD, WSDL. \\
  Developing new features in, and maintaining, a Remote Gaming System (RGS). The RGS is developed for use with common casino games such as Poker and Bingo. Work involves, among other things, integrating the RGS with other RGS and API:s, tweaking the RGS to fit new customer needs.
  
  \item \textbf{Telenor / Bredbandsbolaget} 2010-01-01 to 2013-02-28 \\
  Work involving: Java (Spring Framework, JSF, JSP, J2EE, Tomcat, JUnit, Mockito, PowerMock, JMeter, Maven), CMS (Tridion), XHTML, CSS, JavaScript (JQuery, Prototype, AJAX, JSON, Jersey, Gson), Google Analytics, Omniture, Eclipse, SiteSeeker, CVS, Mercurial, Hudson, Jenkins, TDD, Eclipse. \\
  Developing new features, and maintaining, bredbandsbolaget.se and parts of telenor.se.

  Mixed job doing everything from requirements analysis to actual implementation. Discussing and designing API:s, dsigning and implementing UI for editors, implementing actual UI on the public website...

 \end{itemize}
 
 \item \textbf{Lund Institute of Technology} Spring of 2009\\
 Master thesis on ``Palpable Computing in a Health Care Environment''. A web application was developed. PalCom services and a GUI application was developed. The work involved XML, XSLT, Java, PHP, Apache, MySQL, PalCom.\\

 \item \textbf{Securitas Direct (Malmoe)} Spring of 2009\\
 Employed as PHP developer to maintain internal web applications. Work involved, among other technologies, Linux, Apache, MySQL, PHP, JavaScript and CSS.\\
 
 \item \textbf{Axis Communications AB (HQ Lund)} Summer of 2007\\
 I was mainly working with a web based surveillance system called STS (Subscription Technology Service). The work involved JavaScript, PHP, MVC, MySQL, Apache and Linux. I was doing alot of refactoring involving separating views from controllers and models according to the MVC design pattern. \\
 
 \item \textbf{Bladerman (www.bladerman.com)} Part time 2003-2005\\
 Developer and designer. Work involved PHP, Apache, JavaScript and MySQL. An all new web shop, database and administration pages was produced.\\
\end{itemize}

\end{document}


